\documentclass[a4paper,11pt,twoside]{ThesisStyle}

\usepackage{lmodern}
\usepackage{subfig}
\usepackage{enumitem}
\usepackage{url}
\usepackage{algorithm}
\usepackage{array}
\usepackage[pdftex]{adjustbox}

%\makeatletter
%\setlength{\@fptop}{0pt}
%\makeatother
\include{formatAndDefs}

\begin{document}
%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------
\let\cleardoublepage\clearpage 
\include{TitlePage}

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\begin{vcenterpage}
\noindent\rule[2pt]{\textwidth}{0.5pt}

\noindent{\large\textbf{Abstract:}}
Serious game is used in healthcare to perform patients' rehabilitation and training. An example of such game is Hammer and Planks which is used to rehabilitate patient with balance disorders. Utilizing motion sensing input devices (Kinect, Wii Balance Board), the game is played by moving player's body. However, it is difficult to assess the rehabilitation progress from the game. In this Master thesis we design and develop visualization interface to help healthcare professional make correct diagnostic of patients' progress and therefore enable them to set the difficulty level for future rehabilitation session.
\\
To achieve this objective, we developed a visualization application which enables healthcare professional to analyse gameplay from two different views: (i) Session Visualization which allows analysis on one session. With this view, users are able to identify the frequency of movement related to objects on the game (ii) Summary Visualization which allows movement analysis over several sessions. This view enables users to navigate and explore the evolution of movement throughout all of the sessions. Here we propose a clustering method based on hierarchical clustering to group similar movement pattern over sections of game horizontal x-axis. This view also enables users to analyse in which area of x-axis the movement frequently happened. The proposed visualization is illustrated with two case studies which demonstrate the ability of the application to assess the rehabilitation progress.
\\
{\large\textbf{Keywords:}}
Information Visualization, Visual Analytic, Body Movement Visualization, Movement Analysis, Hierarchical Clustering
\\
\noindent\rule[2pt]{\textwidth}{0.5pt}
\end{vcenterpage}

\dominitoc

\pagenumbering{roman}
\cleardoublepage
%----------------------------------------------------------------------------------------
%	ACKNOWLEDGMENTS
%----------------------------------------------------------------------------------------

\section*{Acknowledgments}

In the name of Allah, the Most Gracious and the Most Merciful.

Alhamdulillah, all praises to Allah for the strengths and His blessings in completing this thesis.

Firstly, I would like to express my sincere gratitude to my advisors Arnaud Sallaberry and Jer\^{o}m\'{e} Az\'{e} for their valuable guidance, detailed feedbacks, and continuous support. Without their help, I wouldn't be able to finish the research and complete the writing of this master thesis. Especially for Arnaud Salaberry, his patience and attention has made the development of the visualization application possible. I would also like to thank my supervisor  Nac\'{e}ra Bennacer for her insightful comments and feedbacks.

I am also thankful to S\'{e}bastien Andary of NaturalPad for his help regarding the Hammer and Planks game as well as providing the game application and data for the research. His valuable support has made the completion of this research possible.

My sincere thanks also goes to the Advanse Team in LIRMM, who gave me the opportunity to join their team as an intern and who provided access to their research facilities. Most importantly, for their understanding and support when I had medical difficulties during my internship.
My immense gratitude towards my colleague for their time and participation in providing the gameplay data set.


My gratitude goes to the IT4BI Consortium for giving me the opportunity and making all of this possible. My gratitude also goes to Universit\'{e} Paul Val\'{e}ry Montpellier for funding the research.

I thank my friends for their company, support and motivation during the past six months. Thank you for the friendship and memories. I would also like to thank my parents for their continuous support and prayers.  

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS, LIST OF FIGURES, LIST OF TABLES
%----------------------------------------------------------------------------------------

\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables

\mainmatter
%----------------------------------------------------------------------------------------
%	CHAPTER
%----------------------------------------------------------------------------------------

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4}
\include{Chapters/Chapter5}
\include{Chapters/Chapter6}
\include{Chapters/Chapter7}
%----------------------------------------------------------------------------------------
%	APPENDICES
%----------------------------------------------------------------------------------------

%\appendix%

%\include{Appendices/Appendix1}%

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\bibliography{Thesis}
\bibliographystyle{plain}


%\printnomenclature

%\cleardoublepage


\end{document}
